\vspace{1.0cm} \LARGE \bf MERS-CoV spillover at the camel-human interface

### 2017-10-23 mers-structure.tex
Address #37
Might be fixed already.

\subsection*{Recombination shapes MERS-CoV diversity}
Recombination has been shown to occur in all genera of coronaviruses, including MERS-CoV \citep{lai_1985,makino_1986,keck_1988,kottier_1995,herrewegh_1998}.
In order to explore the role of recombination in shaping MERS-CoV genetic diversity we used two recombination detection approaches across partitions of taxa corresponding to inferred MERS-CoV clades.
Both methods rely on sampling parental and recombinant alleles within the alignment, although each quantifies different signals of recombination.
One hallmark of recombination is the ability to carry alleles derived via mutation from one lineage to another, which appear as repeated mutations taking place in the recipient lineage, somewhere else in the tree.
The PHI (pairwise homoplasy index) test quantifies the appearance of these excessive repeat mutations (homoplasies) within an alignment \citep{bruen_simple_2006}.
Another hallmark of recombination is spatial clustering of alleles along the genome, due to how template switching, the primary mechanism of recombination in RNA viruses, occurs.
3Seq relies on the spatial structure of nucleotide similarities between sequence triplets -- two potential parent-donors and one candidate offspring-recipient sequences \citep{boni_exact_2007}.

>>>>

\subsection*{Recombination shapes MERS-CoV diversity}
Recombination has been shown to occur in all genera of coronaviruses, including MERS-CoV \citep{lai_1985,makino_1986,keck_1988,kottier_1995,herrewegh_1998}.
In order to explore the role of recombination in shaping MERS-CoV genetic diversity we used two recombination detection approaches across partitions of taxa corresponding to inferred MERS-CoV clades.
Both methods rely on sampling parental and recombinant alleles within the alignment, although each quantifies different signals of recombination.
One hallmark of recombination is the ability to carry alleles derived via mutation from one lineage to another, which appear as repeated mutations taking place in the recipient lineage, somewhere else in the tree.
The PHI (pairwise homoplasy index) test quantifies the appearance of these excessive repeat mutations (homoplasies) within an alignment \citep{bruen_simple_2006}.
Another hallmark of recombination is clustering of alleles along the genome, due to how template switching, the primary mechanism of recombination in RNA viruses, occurs.
3Seq relies on the clustering of nucleotide similarities along the genome between sequence triplets -- two potential parent-donors and one candidate offspring-recipient sequences \citep{boni_exact_2007}.
